The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
extend paragraph about TraceMonkey (thanks arigo)

TraceMonkey, a tracing JIT for JavaScript, uses trace stitching
to avoid the overhead of returning to the trace monitor and calling another
trace when taking a side exit~\cite{Gal:2009ux}. In this approach it is required to write live
values to an activation record before entering the new trace.

>>>>

For TraceMonkey, a tracing JIT for JavaScript, Gal et. al~\cite{Gal:2009ux}
illustrate how it uses a small off-trace set of instructions that is
executed in case a guard failure to return a structure describing the reason
for the exit along with the information needed to restored the interpreter
state. TraceMonkey uses trace stitching to avoid the overhead of returning to
the trace monitor and calling another trace when taking a side exit. In this
approach it is required to write live values to an activation record before
entering the new trace.
